Privacy and Security Benefits of Jailbreaking iOS

### 2013-12-10 final_project/paper.tex
moar paper moar code

>>>>

\subsection{Changing the default iOS root password}

Users with jailbroken devices are advised to change the default root password - the well known "alpine". Since an attacker can install a remote login utility such as SSH and gain full control over the device. In case a device is jailbroken by an attacker, the default password if left unchanged can be used to access the filesystem, bypassing any lock screen passwords the user might have (passwords are stored in \texttt{{\textbackslash}var{\textbackslash}Keychain})\cite{lostpass}
